---
title: "SRP 2020"
author: "Samantha Cavalli"
output: html_notebook
---

```{r}
xbar <- 10

sigma <- 5

n <- 10
```

```{r}
curve(pnorm((mu - xbar)/(sigma/sqrt(n))), from = -20, to = 20, xname = 'mu')
```
p-value for right sided hypothesis test 

mean is a 10, sd = 5/sqrt(10)

```{r}
pnorm(15 - xbar)/(sigma/sqrt(n))
```

```{r}
curve(1-pnorm((mu - xbar)/(sigma/sqrt(n))), from = -20, to = 20, xname = 'mu')
```
p-value for left sided hypothesis test 

```{r}
1-pnorm(15 - xbar)/(sigma/sqrt(n))
```

# 6/23/20
## Weight Loss Data

```{r}
#install.packages("readr")
```

```{r}
library(readr)
```

```{r}
weight.change.data <- read.csv("Downloads/weight_change_data (1).csv")
```

## Low Carb 

```{r}
hist(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"])
```

### Low Carb Confidence Distribution 

```{r}
xbar.lowcarb <- mean(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"])
s.lowcarb <- sd(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"])
n.lowcarb<- length(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"])
```

```{r}
pt.lowcarb <- pt(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"], df= n.lowcarb-1)

pt.lowcarb
```

### Low Carb Confidence Distribution Curve 

```{r}
curve.lowcarb <- curve(1-pt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = n.lowcarb-1), from = -20, to = 0, xname = 'mu')

curve.lowcarb
```

```{r}
curve(1-pt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = n.lowcarb-1), from = -20, to = 0, xname = 'mu')


for (mu in seq(from=-20, to=0, by= 0.5) ) {
  lowcarb.t.test <- t.test(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"], alternative = "greater", mu = mu)
  abline(h=lowcarb.t.test$p.value, v= mu)
  
}

```
Check 

### Low Carb Confidence Curve 

```{r}
cc.lowcarb <- function(mu) abs(2*(1-pt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = (n.lowcarb-1)))-1)
```

```{r}
curve(cc.lowcarb, from = -20, to=0, xname = 'mu')

for (conf.int in seq(from = 0, to= 1, by =0.2)) {
   lowcarb.t.test.2 <- t.test(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"], conf.level= conf.int)
  cc.lowcarb <- function(mu) abs(2*(1-pt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = (n.lowcarb-1)))-1) 
  
   abline(h=conf.int, v= lowcarb.t.test.2$conf.int)
  
}
```



## Low Fat

```{r}
hist(weight.change.data$weightchange[weight.change.data$diet=="Low Fat"])
```

```{r}
xbar.lowfat <- mean(weight.change.data$weightchange[weight.change.data$diet=="Low Fat"])
s.lowfat <- sd(weight.change.data$weightchange[weight.change.data$diet=="Low Fat"])
n.lowfat <- length(weight.change.data$weightchange[weight.change.data$diet=="Low Fat"])
```

### Low Fat Confidence Distribution 

```{r}
curve.lowfat <- curve(1-pt((xbar.lowfat-mu)/(s.lowfat/sqrt(n.lowfat)), df = n.lowfat-1), from = -20, to = 0, xname = 'mu')

curve.lowfat
```

### Low Fat Confidence Curve 

```{r}
cc.lowfat <- function(mu) abs(2*(1-pt((xbar.lowfat-mu)/(s.lowfat/sqrt(n.lowfat)), df = (n.lowfat-1)))-1)

curve(cc.lowfat, from = -20, to=0, xname = 'mu')
```

# 6/24/20

## Low Carb Confidence Density

```{r}
low.carb.conf.dens <- function(mu) 1/(s.lowcarb/sqrt(n.lowcarb))*dt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = n.lowcarb -1)

curve(low.carb.conf.dens(mu), from = -20, to = 0, xname = "mu")
                                    
```

### Check

```{r}
integrate(function(mu) low.carb.conf.dens(mu), lower= -Inf, upper = -13)
```

```{r}
curve(low.carb.conf.dens(mu), from = -20, to = 0, xname = "mu")
```

```{r}
curve.lowcarb <- curve(1-pt((xbar.lowcarb-mu)/(s.lowcarb/sqrt(n.lowcarb)), df = n.lowcarb-1), from = -20, to = 0, xname = 'mu')
for (mu in seq(from = -20, to = 0, by = .5)) {
  int.lowcarb <- integrate(function(mu) low.carb.conf.dens(mu), lower= -Inf, upper = mu)
  
  abline(h= int.lowcarb$value, col = "blue")
  abline(v= mu, col = "red")
  abline(h = 0.5, v= -13.4225)
}
```

# Confidence Distribution for Welch's Two-Sample T-Test

```{r}
welch.curve.lowcarb <- curve(1-pt((xbar.lowcarb-xbar.lowfat-delta)/((s.lowcarb/sqrt(n.lowcarb))+(s.lowfat/sqrt(n.lowfat))), df = 601), from = -20, to = 0, xname = 'delta')

welch.curve.lowcarb
```

## Check Welch Confidence Distribution


```{r}
lowcarb.welch.test <- t.test(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"],weight.change.data$weightchange[weight.change.data$diet=="Low Fat"], alternative = "greater", mu = delta)

lowcarb.welch.test
```

```{r}
curve(1-pt((xbar.lowcarb-xbar.lowfat-delta)/((s.lowcarb/sqrt(n.lowcarb))+(s.lowfat/sqrt(n.lowfat))), df = 603.97), from = -10, to = 10, xname = 'delta')


for (delta in seq(from=-10, to=10, by= 1) ) {
  lowcarb.welch.test <- t.test(weight.change.data$weightchange[weight.change.data$diet=="Low Carb"],weight.change.data$weightchange[weight.change.data$diet=="Low Fat"], alternative = "greater", mu = delta)
  abline(h=lowcarb.welch.test$p.value, v= delta)
  
}

```

# 6/25/20

## Confidence Curve for Two-Sample T-Test

```{r}
cc.two.sample <- function (delta) abs(2*(1-pt((xbar.lowcarb-xbar.lowfat-delta)/((s.lowcarb/sqrt(n.lowcarb))+(s.lowfat/sqrt(n.lowfat))), df = 603.97))-1)

curve(cc.two.sample, from = -10, to = 10, xname = 'delta')
```

## Density for Two-Sample T-Test

```{r}
two.sample.conf.dens <- function(delta) 1/((s.lowcarb/sqrt(n.lowcarb))+(s.lowfat/sqrt(n.lowfat)))*dt((xbar.lowcarb-xbar.lowfat-delta)/((s.lowcarb/sqrt(n.lowcarb)+(s.lowfat/sqrt(n.lowfat)))), df = 603.97)

curve(two.sample.conf.dens(delta), from = -10, to = 10, xname = 'delta')
```

### Check Density 

```{r}
integrate(function(delta) two.sample.conf.dens(delta), lower= -Inf, upper = -5)
```


```{r}
qnorm(0.9995)
```

# t.confdist

```{r}
t.confdist <- function(x, y = NULL, paired = FALSE, plot = TRUE) {

  if(!is.null(y)){
  if(paired)
	    xok <- yok <- complete.cases(x,y)
	else {
	    yok <- !is.na(y)
	    xok <- !is.na(x)
	}
	y <- y[yok]
    } else {
	if (paired) stop("'y' is missing for paired test")
	xok <- !is.na(x)
	yok <- NULL
    }
    x <- x[xok]
    if (paired) {
	x <- x-y
	y <- NULL
    }
  
  xbar <- mean(x)
  sx <- sd(x)
  nx <- length(x)
  vx <- var(x)
  
  if(is.null(y)){
  # Confidence Distribution 
  
  x1.dist.func <- function(mu) 1-pt((xbar - mu)/(sx/sqrt(nx)), df = (nx-1))
  
  # Confidence Density
  
  x1.dens.func <- function(mu) (1/(sx/sqrt(nx)))*(dt((xbar-mu)/((sx/sqrt(nx))), df=(nx-1)))

  # Confidence Curve
  
  x1.conf.curv.func <- function(mu) abs(2*(1-pt((xbar - mu)/(sx/sqrt(nx)), df = (nx-1)))-1)
  
  # Confidence Quantile
  
  x1.quantile.func <- function(p) xbar + (sx/sqrt(nx))*qt(p, df = (nx-1))
  
  x.list <- list(pconf = x1.dist.func, dconf = x1.dens.func, cconf = x1.conf.curv.func, qconf = x1.quantile.func)
  
  
  if(plot == TRUE){
  
    t.crit <- qt(0.9995, df = nx-1)
    curve(x1.dist.func(mu), from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Distribution")
    curve(x1.dens.func(mu), from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Density")
    curve(x1.conf.curv.func, from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Curve")

  }
  
  return(x.list)
  
  } else if (!is.null(y)){
    
  ybar <- mean(y)
  sy <- sd(y)
  ny <- length(y)
  vy <- var(y)
  stderrx <- sqrt(vx/nx)
	stderry <- sqrt(vy/ny)
	stderr <- sqrt(stderrx^2 + stderry^2)
	df.welch <- stderr^4/(stderrx^4/(nx-1) + stderry^4/(ny-1))
	
	# Confidence Distribution 
	welch.dist.func <- function(delta) 1-pt((xbar - ybar - delta)/(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), df = df.welch)

		# Confidence Density
	welch.dens.func <- function(delta) (1/sqrt((sx^2/(nx))+(sy^2/(ny)))*(dt((xbar - ybar- delta)/sqrt((sx^2/(nx))+(sy^2/(ny))), df=df.welch)))

	# Confidence Curve
  welch.conf.curv.func <- function(delta) abs(2*(1-pt((xbar - ybar - delta)/(sqrt((((s.lowcarb)^2)/n.lowcarb)+((s.lowfat)^2)/n.lowfat)), df = df.welch))-1)
  
  # Confidence Quantile
  welch.quantile.func <- function(p) (xbar - ybar) + sqrt((sx^2/(nx))+(sy^2/(ny)))*qt(p, df = df.welch)
  
  welch.list <- list(pconf = welch.dist.func, dconf = welch.dens.func, cconf =  welch.conf.curv.func, qconf = welch.quantile.func)
  
	if(plot == TRUE){
  
	  t.crit <- qt(0.9995, df = nx-1)  
  
	  curve(welch.dist.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Distribution")
    curve(welch.dens.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Density")
    curve(welch.conf.curv.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Curve", ylab = "Level of Confidence")
 
	}
  return(welch.list)

  }
}
```

# t.confdist.summary

```{r}
t.confdist.summary <- function(x,y,n, plot = TRUE){
 
stopifnot(length(x)==length(y) && length(x)==length(n))
  
if (length(x)==1){
  xbar <- x[1]
  sx <- y[1]
  nx <- n[1]
  vx <- sx^2
  
   # Confidence Distribution 
  
  x1.dist.func <- function(mu) 1-pt((xbar - mu)/(sx/sqrt(nx)), df = (nx-1))
  
  # Confidence Density
  
  x1.dens.func <- function(mu) (1/(sx/sqrt(nx)))*(dt((xbar-mu)/((sx/sqrt(nx))), df=(nx-1)))

  # Confidence Curve
  
  x1.conf.curv.func <- function(mu) abs(2*(1-pt((xbar - mu)/(sx/sqrt(nx)), df = (nx-1)))-1)
  
  # Confidence Quantile
  
  x1.quantile.func <- function(p) xbar + (sx/sqrt(nx))*qt(p, df = (nx-1))
  
  x.list <- list(pconf = x1.dist.func, dconf = x1.dens.func, cconf = x1.conf.curv.func, qconf = x1.quantile.func)
  
 if(plot == TRUE){
  
    t.crit <- qt(0.9995, df = nx-1)
    curve(x1.dist.func(mu), from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Distribution")
    curve(x1.dens.func(mu), from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Density")
    curve(x1.conf.curv.func, from = xbar - t.crit*(sx/sqrt(nx)), to = xbar + t.crit*(sx/sqrt(nx)), xname = "mu", main = "Confidence Curve")

  }
  
  return(x.list)
  
  } else if (length(x)==2){  
    xbar <- x[1]
    sx <- y[1]
    nx <- n[1]
    vx <- sx^2
    ybar <- x[2]
    sy <- y[2]
    ny <- n[2]
    vy <- sy^2
    stderrx <- sqrt(vx/nx)
    stderry <- sqrt(vy/ny)
    stderr <- sqrt(stderrx^2 + stderry^2)
    df.welch <- stderr^4/stderrx^4/(nx-1) + stderry^4/(ny-1)

	# Confidence Distribution 
	welch.dist.func <- function(delta) 1-pt((xbar - ybar - delta)/(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), df = df.welch)

		# Confidence Density
	welch.dens.func <- function(delta) (1/sqrt((sx^2/(nx))+(sy^2/(ny)))*(dt((xbar - ybar- delta)/sqrt((sx^2/(nx))+(sy^2/(ny))), df=df.welch)))

	# Confidence Curve
  welch.conf.curv.func <- function(delta) abs(2*(1-pt((xbar - ybar - delta)/(sqrt((((s.lowcarb)^2)/n.lowcarb)+((s.lowfat)^2)/n.lowfat)), df = df.welch))-1)
  
  # Confidence Quantile
  welch.quantile.func <- function(p) (xbar - ybar) + sqrt((sx^2/(nx))+(sy^2/(ny)))*qt(p, df = df.welch)
  
  welch.list <- list(pconf = welch.dist.func, dconf = welch.dens.func, cconf =  welch.conf.curv.func, qconf = welch.quantile.func)
  
	if(plot == TRUE){
  
	  t.crit <- qt(0.9995, df = nx-1)  
  
	  curve(welch.dist.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Distribution")
    curve(welch.dens.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Density")
    curve(welch.conf.curv.func, from = (xbar-ybar) - t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), to = (xbar-ybar) + t.crit*(sqrt((((sx)^2)/nx)+((sy)^2)/ny)), xname = "delta", main = "Confidence Curve", ylab = "Level of Confidence")
}
return(welch.list)
 
  }else{
    stop("vector lengths must be equal to or less than 2")
  }
  
}
```

# Testing with weight loss data

```{r}
xbar.lowcarb.bmi <- -2.07
xbar.lowfat.bmi <- -1.75
s.lowfat.bmi <- (-1.97-(xbar.lowfat.bmi))*sqrt(n.lowfat)/(qt(0.975,df=n.lowfat-1))
s.lowcarb.bmi <- (-2.3-(xbar.lowcarb.bmi))*sqrt(n.lowcarb)/(qt(0.975, df = n.lowcarb-1))

s.lowcarb.bmi
s.lowfat.bmi
```

# Testing with lowfat data

```{r}
conf.lowfat.bmi <- t.confdist.summary(x=xbar.lowfat.bmi, y=s.lowfat.bmi, n=n.lowfat)
abline(h=0.95)
abline(v=-1.97)
abline(v=-1.52)
```

# Testing with low carb data

```{r}
conf.lowcarb.bmi <- t.confdist.summary(x=xbar.lowcarb.bmi, y=s.lowcarb.bmi, n=n.lowcarb)
abline(h=0.95)
abline(v=-2.3)
abline(v=-1.85)
```

# Testing both 

```{r}
conf.lowcarb.lowfat.bmi <- t.confdist.summary(x=c(xbar.lowcarb.bmi, xbar.lowfat.bmi), y=c(s.lowcarb.bmi,s.lowfat.bmi), n=c(n.lowcarb,n.lowfat))
```

